Holomorphic field theories and higher algebra

### 2024-09-14 draft.tex
rearranging holo field theory section

A reader could read this core section independently of the rest of the paper,
as it focuses on algebra and geometry and requires no substantial knowledge of field theory {\it per se}.

@@

\brian{complex geometry, dolbeault, dg stuff.}

@@

\subsection{Definitions}

@@

>>>>

A reader could read this core portion independently of the rest of the paper,
as it focuses on algebra and geometry and requires no substantial knowledge of field theory {\it per se}.

@@

\owen{I rearranged this section somewhat. Our discussion of examples did not involve any BRST/BV stuff, so I put it right after the impressionistic opening. The "definitions" section seemed to be purely perturbative and to use notions from derived geometry, so I put it next. It should be fleshed out a little (e.g., a mention of the "fundamental theorem of deformaiton theory" and maybe show how to write one of the examples in that language).}

We begin by sketching what a classical field theory is, somewhat impressionistically, and then offer some concrete examples.

@@

@@

\subsection{Perturbative field theories via derived deformations}
